### 2015-02-28 icfp15-servo/browsers.tex
Update figure 1.

Modern web browsers do not just load static pages, but can also handle pages that have similar
complexity to native applications.
From application suites such as the Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine\footnote{\url{https://www.unrealengine.com/}},
modern browsers have the ability to handle much more than simple static pages.
\figref{fig:browser} shows the steps in processing a site.
While the naming is specific to the Servo browser, similar steps are used in all modern browsers.\footnote{\url{http://www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}[ht]
  \begin{center}
    \includegraphics[scale=0.7]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%

@@

@@

After constructing the DOM and determining the set of styles defined in the Cascading Style Sheets (CSS) that has
been loaded, those styles are applied to the DOM and a new flow tree that represents the elements is created.
This process can create many more flows than previously existed in the DOM --- for example, when a list item is
styled to have an associated counter glyph.

\subsection{Display}

That tree of elements, called the \emph{flow tree} in Servo, is then processed
to produce a set of \emph{display list} items.  These list items are the
actual graphical elements, text runs, etc. in their final on-screen positions.
The order in which these elements are displayed is well-defined by the
standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.

@@

The set of memory buffers or graphical surfaces, called layers, are then
transformed and composited together to form a final image for
presentation.

>>>>

Modern web browsers do not just load static pages, but can also handle pages that have similar
complexity to native applications.
From application suites such as the Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine\footnote{\url{https://www.unrealengine.com/}},
modern browsers have the ability to handle much more than simple static pages.
\figref{fig:browser} shows the steps in processing a site.
While the naming is specific to the Servo browser, similar steps are used in all modern browsers.\footnote{\url{http://www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}[ht]
  \begin{center}
    \includegraphics[scale=0.5]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%

@@

\subsection{Styling}

After constructing the DOM, the browser uses the styling information in linked
CSS files and in the HTML to compute a styled tree of flows and fragments,
called the \emph{flow tree} in Servo.
This process can create many more flows than previously existed in the DOM ---
for example, when a list item is styled to have an associated counter glyph.

@@

The flow tree is then processed to produce a set of \emph{display list} items.
These list items are the actual graphical elements, text runs, etc. in their
final on-screen positions.
The order in which these elements are displayed is well-defined by the
standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.

@@

The set of memory buffers or graphical surfaces, called \emph{layers}, are then
transformed and composited together to form a final image for
presentation. Layerization is used to optimize interactive transformations
like scrolling and certain animations.
